QOCO: A QoE-Oriented Computation Offloading Algorithm based on Deep Reinforcement Learning for Mobile Edge Computing

### 2023-10-21 paper.tex
update files

\begin{figure}[tbp]
	\captionsetup{name=Fig.}
	\begin{minipage}[b]{0.50\linewidth}
		\centering
		\includegraphics[width=\textwidth]{222} 		
		\textcolor{white}{i}\hspace{0.6cm}(a)
	\end{minipage}
	\hspace{-0.2cm}
	\begin{minipage}[b]{0.50\linewidth}
		\centering
		\includegraphics[width=\textwidth]{223}
		\textcolor{white}{i}\hspace{0.6cm}(b)
	\end{minipage}
	\vspace{-0.7cm}
	\caption{The overall energy consumption under different computation workloads: (a) task arrival rate; (b) the number of MDs.}
	\label{chart2}
\end{figure}
Fig.~\ref{chart2} (a) and ~\ref{chart2} (b) illustrate the overall energy consumption for different values of task arrival rate and the number of MDs, respectively. At the lower task arrival rate, the total energy consumption of all methods is close to each other. When the task arrival rate increases, the total energy consumption of each method increases differently. It can be found that the production of more computational tasks leads to a continuous increase in energy consumption until the capacity is saturated, and the energy consumption remains constant at its maximum. The QOCO algorithm takes into account the battery level of the MD in its decision-making process. At task arrival rate 450, QOCO effectively reduces overall energy consumption by 18\% and 15\% compared to RD and PGOA, respectively. However, it consumes more energy compared to LC and FC because they do not utilize the full capacity (LC uses the MD's computational resources, while FC utilizes the transmission link and allocated capacity from EN to MD).
 \begin{figure}[tbp]
	\captionsetup{name=Fig.}
	\begin{minipage}[b]{0.50\linewidth}
		\centering
		\includegraphics[width=\textwidth]{333} 		
		\textcolor{white}{i}\hspace{0.6cm}(a)
	\end{minipage}
	\hspace{-0.2cm}
	\begin{minipage}[b]{0.50\linewidth}
		\centering
		\includegraphics[width=\textwidth]{334}
		\textcolor{white}{i}\hspace{0.6cm}(b)
	\end{minipage}
	\vspace{-0.7cm}
	\caption{The average delay under different computation workloads: (a) task arrival rate; (b) the number of MDs.}
	\label{chart3}
\end{figure} 
In Fig.~\ref{chart2} (b), an increasing trend in overall energy consumption is observed as the number of MDs increases. With the increase in MDs, the number of resources available in the system increases, which leads to higher energy consumption in the system. The QOCO algorithm consistently outperforms the benchmark methods in overall energy consumption, especially when the number of MDs is large. Specifically, QOCO demonstrates a 27\% and 16\% reduction in overall energy consumption compared to RD and PGOA, respectively, when the number of MDs increases to 110.

@@

In this paper, we focused on addressing the challenge of offloading in MEC systems, where strict task processing deadlines and energy constraints adversely impact system performance. We formulated an optimization problem that aims to maximize the QoE of each MD individually, while QoE reflects the energy consumption and task completion delay. To address the dynamic and uncertain mobile environment, we proposed a QoE-oriented DRL-based computation offloading algorithm called QOCO. Our proposed algorithm empowers MDs to make offloading decisions without relying on knowledge about task models or other MDs' offloading decisions. The QOCO algorithm not only adapts to the uncertain dynamics of load levels at ENs, but also effectively manages the ever-changing system environment. Through extensive simulations, we demonstrated that QOCO outperforms several established benchmark techniques. Specifically, QOCO increases the average user's QoE by XX\% compared to an existing work. This advantage can lead to improvements in key performance metrics, including task completion rate, task delay, and energy consumption, under different system conditions and varying user demands.

>>>>

\begin{figure}[tbp]
	\captionsetup{name=Fig.}
	\begin{minipage}[b]{0.50\linewidth}
		\centering
		\includegraphics[width=\textwidth]{222} 		
		\textcolor{white}{i}\hspace{0.6cm}(a)
	\end{minipage}
	\hspace{-0.2cm}
	\begin{minipage}[b]{0.50\linewidth}
		\centering
		\includegraphics[width=\textwidth]{223}
		\textcolor{white}{i}\hspace{0.6cm}(b)
	\end{minipage}
	\vspace{-0.7cm}
	\caption{The overall energy consumption under different computation workloads: (a) task arrival rate; (b) the number of MDs.}
	\label{chart2}
\end{figure}
Fig.~\ref{chart2} (a) and ~\ref{chart2} (b) illustrate the overall energy consumption for different values of task arrival rate and the number of MDs, respectively. At the lower task arrival rate, the total energy consumption of all methods is close to each other. When the task arrival rate increases, the total energy consumption of each method increases differently. It can be found that the production of more computational tasks leads to a continuous increase in energy consumption until the capacity is saturated, and the energy consumption remains constant at its maximum. The QOCO algorithm takes into account the battery level of the MD in its decision-making process. In Fig.~\ref{chart2} (a), at task arrival rate 450, QOCO effectively reduces overall energy consumption by 18\% and 15\% compared to RD and PGOA, respectively. However, it consumes more energy compared to LC and FC because they do not utilize the full capacity (LC uses the MD's computational resources, while FC utilizes the transmission link and allocated capacity from EN to MD).
 \begin{figure}[tbp]
	\captionsetup{name=Fig.}
	\begin{minipage}[b]{0.50\linewidth}
		\centering
		\includegraphics[width=\textwidth]{333} 		
		\textcolor{white}{i}\hspace{0.6cm}(a)
	\end{minipage}
	\hspace{-0.2cm}
	\begin{minipage}[b]{0.50\linewidth}
		\centering
		\includegraphics[width=\textwidth]{334}
		\textcolor{white}{i}\hspace{0.6cm}(b)
	\end{minipage}
	\vspace{-0.7cm}
	\caption{The average delay under different computation workloads: (a) task arrival rate; (b) the number of MDs.}
	\label{chart3}
\end{figure} 
In Fig.~\ref{chart2} (b), an increasing trend in overall energy consumption is observed as the number of MDs increases. With the increase in MDs, the number of resources available in the system increases, which leads to higher energy consumption in the system. The QOCO algorithm consistently outperforms the benchmark methods in overall energy consumption, especially when the number of MDs is large. Specifically, QOCO demonstrates a 27\% and 16\% reduction in overall energy consumption compared to RD and PGOA, respectively, when the number of MDs increases to 110.

@@

In this paper, we focused on addressing the challenge of offloading in MEC systems, where strict task processing deadlines and energy constraints adversely impact system performance. We formulated an optimization problem that aims to maximize the QoE of each MD individually, while QoE reflects the energy consumption and task completion delay. To address the dynamic and uncertain mobile environment, we proposed a QoE-oriented DRL-based computation offloading algorithm called QOCO. Our proposed algorithm empowers MDs to make offloading decisions without relying on knowledge about task models or other MDs' offloading decisions. The QOCO algorithm not only adapts to the uncertain dynamics of load levels at ENs, but also effectively manages the ever-changing system environment. Through extensive simulations, we demonstrated that QOCO outperforms several established benchmark techniques. Specifically, QOCO increases the average user's QoE by 37\% compared to an existing work. This advantage can lead to improvements in key performance metrics, including task completion rate, task delay, and energy consumption, under different system conditions and varying user demands.
